Towards Atomistic Resolution Structure of Phosphatidylcholine Headgroup and Glycerol Backbone at Different Ambient Conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-10-13 HGmodelMANUSCRIPT/REPLYtoREVIEWER2.txt

Reviewer 2.

We thank for the very positive feedback. The errors in English are
now fixed as suggested.

Reviewer 1.

1.
Author reply:
In the publications mentioned by the reviewer it is shown that the
the membrane properties are affected by interfacial tension rather than the ensemble. 
This is also explicitly said in the abstract of
J. Chem. Phys. 111, 1281-1287
"Equivalence between the constant area and constant surface tension ensembles is
investigated by comparing the present simulations with earlier work from our laboratories and we
find simulation results to depend much more strongly on the specified surface area or surface tension
than on the ensemble employed"
It should be also noted that the total lengths of the simulations are around 1ns 
in the mentioned publications while our simulations are 1-2 orders of magnitude longer. 
Thus, even though the dependence on the ensemble would be observed in these short simulations
it could very well be due to insufficient sampling.

As we have already pointed out we have restricted our work to the available models and
the improvement of these models has been left for further studies. Since all the developers
of the tested models have used NPT ensemble in zero tension, there seems to be consensus on 
this.

It is also much more likely that the force field parameters affect the glycerol backbone and
choline structures much more than the used ensemble or interfacial tension. We have 
left the more detailed discussion on the force field parameters for further studies, 
thus the same should be done for the discussion about ensemble and surface tension which
is most likely less relevant.

2.
Author reply:
All the "subjective sweet spots" in Fig. 2 have exactly the same size: 0.04 units.

@@

This size was agreed on based on the high experimental repeatibility of the order
parameters that we discuss in the text (p12): "Almost all the reported values are
within a variation of ±0.02 [...] for all fully hydrated PC bilayers, regardless
of variation in their acyl chain composition and temperature."

To make the definition of the sweet spots clear to the reader, we now explicitly
point this out when introducing them in the text (p15):

### 2015-10-13 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Change to title case

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[An \textsf{achemso} demo]
  {Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The document title should be given as usual. Some journals require
%% a running title from the author: this should be supplied as an
%% optional argument to \title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[An \textsf{achemso} demo]
  {Towards Atomistic Resolution Structure of Phosphatidylcholine Headgroup and Glycerol Backbone at Different Ambient Conditions\footnote{Publication about results presented in the NMRlipids project}}
